{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-10-31 main.tex
Auto stash before merge of "main" and "origin/main"

	\subsection{Detailed Draft}
	\begin{itemize}
		\item Motivate random functions from introduction and the general concept of random variables
		\item Formalize random function in this context as random variables realizing in a Hilbert space
		\item Introduce $\mathbf{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
		\item Specialize to Hilbert space being $\mathbf{L}^2[0,1]$ for this context
		\item Define mean and covariance function of a random function realizing in $\mathbf{L}^2[0,1]$
		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbf{L}^2[0,1]$
		\item Introduce b-spline and Fourier bases
		\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
		\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbf{L}^2[0,1]$
		\item Explain the concept of iid data in a functional setting
		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
		\item Explain approximations of functional observations using truncated basis representations
		\item Introduce linear operator $L_1$ and sufficient condition associated with it
		\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
	\end{itemize}

There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ because this function also needs to have a useful interpretation. Without it, there might be prediction of the scalar responses from new explanatory functions, but the increase in understanding of the underlying question will be minimal. Thereby, intervals with larger values of $|\beta(s)|$ will contribute more to the response than small values of  $|\beta(s)|$. The sign of $\beta(s)$ indicates either negative or positive influence of $X(s)$ for a specific value of s. To get a useful interpretation, the estimate $\beta$ should not jump in a seemingly random fashion, because a useful interpretation of this erratic behavior will often be impossible and predictions from these model tend to have larger variances and to center around the mean of the responses.

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	Assuming a data generating process of the form:
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects. Define therefore
    \begin{equation}
  	c_{\mathbf{X}}(t,s) = E[\mathbf{X}(t)\mathbf{X}(s)],\: c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\mathbf{Y}], 
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,ds \ +\epsilon]
   \end{equation}
    \begin{equation}
     c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, ds \: | \: X]  + E[\epsilon |\mathbf{X}]
  	\end{equation}
   	\begin{equation}
    	c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,ds
   \end{equation}

>>>>

	\subsection{Detailed Draft}
	\begin{itemize}
		\item Motivate random functions from introduction and the general concept of random variables
		\item Formalize random function in this context as random variables realizing in a Hilbert space
		\item Introduce $\mathbf{L}^2[0,1]$ as the Hilbert space of square integrable functions on $[0,1]$
		\item Specialize to Hilbert space being $\mathbf{L}^2[0,1]$ for this context
		\item Define mean and covariance function of a random function realizing in $\mathbf{L}^2[0,1]$
		\item Introduce the concept of a basis of a Hilbert space and specialize to $\mathbf{L}^2[0,1]$
		\item Introduce b-spline and Fourier bases
		\item Introduce eigenfunctions and FPCA on the basis of covariance function (Karhunen-Lo\'{e}ve expansion)
		\item explain similarities to Eigenvalues and Eigenvectors of matrix + PCA (fraction of explained variance etc...)
		\item Introduce functional observations in this context as realizations of a random variable realizing in $\mathbf{L}^2[0,1]$
		\item Explain the concept of iid data in a functional setting
		\item Define point-wise mean (sample), point-wise standard deviation (sample) and sample covariance function
		\item Explain approximations of functional observations using truncated basis representations
		\item Introduce linear operator $L_1$ and sufficient condition associated with it
		\item Motivate Scalar-on-function regression from multivariate linear regression with a scalar response variable
	\end{itemize}
\subsection{Kokoszka Reimherr (2017) p51-53}
There are several important aspects of functional regression in this functional setting that separate it from usual multiple regression according to \cite{kokoszka_introduction_2017}: In functional linear regression, the aim is not only to obtain an estimate of the function $\beta(s)$ — this estimate also needs to have a useful interpretation. Without it, there might be prediction, but the increase in understanding of the underlying question will be minimal. One aspect of a useful interpretation is that the estimate $\beta$ should not jump in a seemingly random fashion, because an interpretation of this erratic behavior will often be impossible.

	\begin{itemize}
		\item Explain problem of naively extending multivariate linear regression to infinite dimensions
	\end{itemize}
	A common setting in non-functional regression is akin to the following. Assume a data generating as follows:
	\begin{equation}
		Y = X\beta + \epsilon
	\end{equation}
	where $X$ is a vector of random variables, $\beta = (\beta_0, \dots, \beta_J)'$ is a coefficient vector and $epsilon$ is an

	Assuming a data generating process of the form:
	\begin{equation}
     Y =  \int \beta(s)X(s) \,dt \ +\epsilon
    \end{equation}
    it becomes clear that we cannot compute the estimate of $\beta(t)$ as we would do in a classical multivariate setup because of the infinite dimensionality of the underlying objects. Define therefore
    \begin{equation}
  	c_{\mathbf{X}}(t,s) = E[\mathbf{X}(t)\mathbf{X}(s)],\: c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\mathbf{Y}], 
    \end{equation}
   Under the assumption that $X$ is independent from $\epsilon$ we obtain
   \begin{equation}
     c_{\mathbf{X}\mathbf{Y}}(t) = E[\mathbf{X}(t)\int \beta(t)\mathbf{X}(s) \,ds \ +\epsilon]
   \end{equation}
    \begin{equation}
     c_{\mathbf{X}\mathbf{Y}}(t) = E[\int \beta(s) \: \mathbf{X}(s)\mathbf{X}(t) \, ds \: | \: X]  + E[\epsilon |\mathbf{X}]
  	\end{equation}
   	\begin{equation}
    	c_{\mathbf{X}\mathbf{Y}}(t) = \int c_{\mathbf{X}}(t,s) \beta(s) \,ds
   \end{equation}
